Hierarchical models and sequential model fits

### 2025-07-22 documentation/example.qmd
continue cleaning example quarto

```{r}
#| include: false
library(here)
library(tidyverse)
library(ggplot2)
library(haven)
library(stringr)
library(cmdstanr)
library(truncnorm) # for inits
library(bayesplot) # diagnostic plots
devtools::load_all(here::here())
```

@@

```{r}
hier_data <- hierarchical_data(geo_unit_index, hierarchical_level)
names(hier_data)
hier_data

@@

```{r}
plot_prior_post_sigmas(fit = fit_globalsubnat, parname = "mu")

@@

Note that values of sigmas for higher levels are the same in the global national and subnational fit. However, mu_raws may be different if different countries were included or ordered differently. (this is documented inand reproducable with fit_global$geo_unit_index )
```{r}
fit_globalsubnat$post_summ %>%
  filter(variable_no_index == "mu_sigma")
fit1a$post_summ %>%
  filter(variable_no_index == "mu_sigma")
```

>>>>

```{r}
#| include: false
library(here)
library(tidyverse)
library(ggplot2)
library(haven)
library(stringr)
library(cmdstanr)
library(truncnorm) # for inits
library(bayesplot) # diagnostic plots
library(posterior) # else error for as_draws_list
devtools::load_all(here::here())
```

@@

```{r}
hier_data <- hierarchical_data(geo_unit_index, hierarchical_level)
names(hier_data)
# hier_data # not printing, model matrix is too large, see toy example instead

@@

```{r}
plot_prior_post_sigmas(fit = fit_global, parname = "mu")

@@

Note that values of sigmas for higher levels are the same in the global national and subnational fit. However, mu_raws may be different if different countries were included or ordered differently. (this is documented in and reproducable with fit_global$geo_unit_index )
```{r}
fit_globalsubnat$post_summ %>%
  filter(variable_no_index == "mu_sigma")
fit_global$post_summ %>%
  filter(variable_no_index == "mu_sigma")
```
